DynaProg for Scala

### 2013-01-20 docs/report/conclusion.tex
Nits pre-rework.

% ------------------------------------------------------------------------------------------------
\section{Future work}
We consider several directions and possible extensions for our work. We briefly describe each of them and give an idea of how they could be implemented:\ol
\item \textbf{Non-serial scheduling for problems larger than the device memory:} as described in \ref{ns_mem_transfer}, it could be possible to handle problems that are larger than the device memory in an efficient way, thereby dramatically reducing the memory transfer penalties introduced by the main memory usage. However, this comes at the price of a more involved kernel scheduling and a complex element indexing strategy (since we first need to find the enclosing matrix block before addressing the element relatively to it).
\item \textbf{Algorithmic analysis:} so far, we considered that the DSL user would write an optimal program. Another direction in which we could improve the parsers is the recurrence analysis, either by removing serial dependencies when possible (see \ref{calc_simplifications}) or reducing the algorithmic complexity by creating intermediate tabulations (see \ref{user_lang}). These analysis would certainly involve a strong mathematical analysis and the ratio benefit over implementation complexity would be quite small under the initial assumption that the DSL users are experts in their field (thereby knowing how to optimize manually the grammar).
\item \textbf{Serial problems larger than memory:} As discussed in \ref{serial_memory}, this class of problems require a completely different implementation. Since the authors of \cite{swat_mega} are planning to write extensions to their implementation, duplicating the effort might not be worth the price; however, would their future implementation be sufficiently modular, we could integrate it in our framework and redirect compatible grammars to this state of art implementation.
\item \textbf{Add FPGA as target platform:} Initially envisioned a second target platform by George Nithin, a PhD student of the LAP (Laboratory of processors architecture), the underlying complexity of transforming DP recurrences into VHDL code made us leave this platform aside for the scope of this project. The reconfigurability possibilities of FPGA make them attractive whenever it comes to very simple and massively parallel computations where the memory can be pipelined; this makes serial dynamic programming problems good candidates for such implementation.
\item \textbf{Multi-dimensional matrices and independent computations:} In the current implementation, all the matrices are encoded such that they are of the same size. Leveraging the yield analysis, we could reduce the dimension of matrices that are of smaller dimension (for tabulations with bounded maximal size). In the problems we have analyzed, no such special case appeared, this is why we do not support this optimization at present.

>>>>

% ------------------------------------------------------------------------------------------------
\section{Future work}
We consider several directions and possible extensions for our work. We briefly describe each of them and give an idea of how they could be implemented:\ol
\item \textbf{Non-serial scheduling for problems larger than the device memory:} as described in \ref{ns_mem_transfer}, it could be possible to handle problems that are larger than the device memory in an efficient way, thereby dramatically reducing the memory transfer penalties introduced by the main memory usage. However, this comes at the price of a more involved kernel scheduling and a complex element indexing strategy (since we first need to find the enclosing matrix block before addressing the element relatively to it).
\item \textbf{Algorithmic analysis:} so far, we considered that the DSL user would write an optimal program. Another direction in which we could improve the parsers is the recurrence analysis, either by removing serial dependencies when possible (see \ref{calc_simplifications}) or reducing the algorithmic complexity by creating intermediate tabulations (see \ref{user_lang}). These analysis would certainly involve a strong mathematical analysis and the ratio benefit over implementation complexity would be quite small under the initial assumption that the DSL users are experts in their field (thereby knowing how to optimize manually the grammar).
\item \textbf{Serial problems larger than memory:} As discussed in \ref{serial_memory}, this class of problems require a completely different implementation. Since the authors of \cite{swat_mega} are planning to write extensions to their implementation, duplicating the effort might not be worth the price; however, would their future implementation be sufficiently modular, we could integrate it in our framework and redirect compatible grammars to this state of art implementation.
\item \textbf{Add FPGA as target platform:} Initially envisioned a second target platform, the underlying complexity of transforming DP recurrences into VHDL code made us leave this platform aside for the scope of this project. The reconfigurability possibilities of FPGA make them attractive whenever it comes to very simple and massively parallel computations where the data can be pipelined; this makes serial dynamic programming problems good candidates for such implementation.
\item \textbf{Multi-dimensional matrices and independent computations:} In the current implementation, all the matrices are encoded such that they are of the same size. Leveraging the yield analysis, we could reduce the dimension of matrices that are of smaller dimension (for tabulations with bounded maximal size). In the problems we have analyzed, no such special case appeared, this is why we do not support this optimization at present.
